\sysfull

### 2017-11-16 paper/evaluation.tex
removed 'except sort'
removed problematic header
evaluation section revised up to section 7.2

\subsection{Methodology}
\label{sec:results_hardware}

We evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp} energy-harvesting
platform build around a MSP430FR5969~\cite{wolverine} MCU with 64kB of FRAM.
We used a TI Flash Emulation Tool (FET)~\cite{fet} as a power supply during
experiments with continuous power.  For energy measurements, we used
EDB~\cite{edb}.  In experiments with wireless power, we powered the WISP using
an RFID reader (Impinj R1000 with firmware version
3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ
8\,dBic~\cite{atlas2015}. We ccontrolled the RFID reader from a workstation
running Ubuntu 10.4 using \emph{sllurp}~\cite{sllrp_github}.  We set the
transmitted power of the RFID reader to 30\,dBm at 915\,MHz center frequency.
For distance-controlled experiments, we affixed the WISP at varying lengths to
hollow paper tubes placed flat on a lying antenna. We did timing measurements
using the Salea~\cite{saleae} logic analyzer.

For some experiments (noted below) we used an alternative setup where the
MSP-TS430RGZ48C launchpad was used for continuous power experiments. We used
internal timer for measuring run time. For harvested energy, we used
WISP\,5.0~\cite{wisp5,wisp} hardware and ThingMagic Astra-EX integrated RFID
reader set at 30\,dBm transmission power at 915\,MHz.  We used EDB~\cite{edb}
to measure run time. Applications were cross-compiled using GCC and Clang,
allowing us to use LLVM for the \sys compiler. We used version 3.8.0 of both
Clang and LLVM.

@@

We evaluated \sys using benchmarks from the literature~\cite{chain,alpaca} and
several new programs: (i) \textbf{bc}: counts bits in byte pseudo-random string
using several algorithms, and compares results for correctness; (ii)
\textbf{cem}, which emulates an embedded temperature sensing engine and in
which measurements are randomly generated and compressed using LZW with a fixed
entry dictionary and fixed byte block; (iii) \textbf{cuckoo}: which implements
a Bloom-filter-like Cuckoo filter that first hashes a sequence of pseudo-random
numbers, then queries the filter to recover the sequence; (iv) \textbf{rsa}:
which encrypts a fixed string with a stored key; (v) \textbf{ar}: which
performs nearest neighbour classification of randomly generated data modeling a
three-axis accelerometer.  This set of benchmarks overlaps with those used
in~\cite{chain,alpaca}. We implemented several new applications: (vi)
\textbf{sort}: selection sort algorithm on a fixed sequence of numbers, and
(vii) \textbf{dft}: discrete Fourier transform. All applications are compared
in columns eight and nine of Table~\ref{table:compiler_result} showing the
number of source lines of code compared to Chain.

@@

We evaluated \sys to show that it is easy to use and efficient across our
benchmarks.  We evaluate \sys's ease of use by characterizing \sys's automatic
task compiler.  We evaluate \sys efficiency by comparing its runtime
performance to Chain.  We characterize \sys by studying how its performance
varies due to coalescing and when using automatic task compilation versus
manual task compilation.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalescing}
	\caption{\sys coalescing performance measured per application on fixed power (left-most bar per application) and at 20 cm and 40 cm from the RFID reader (center and right-most two bars per application) compared to \sys without coalescing.}
	\label{fig:coalescing}
\end{figure}

@@

We evaluated the effect that paging with different page sizes has on \sys's
performance and we show data in Figure~\ref{fig:page_size}. We show two plots:
the top plot shows the run time performance normalized to the best
per-application performance, using pages of different sizes in \sys, indicated
with the labels on top of each cem bar; the bottom plot shows the number of
page faults for the same set of executions normalized to the maximum of each
set.
%
We measured performance as MCU clock cycles using values read out by TI's CCS
IDE. 
%
The results show a clear ``bathtub curve'' in the performance of each
application, as the number of page faults varies. The data show that across
application there is a page size that minimizes \emph{both} execution time.  We
observe that the page size is not the same for each application, although 64
byte pages perform well for all applications except sort. The increased rate of
page faults is responsible for the overhead with small page sizes; smaller
pages require accessing more different pages, leading to higher paging costs.
With larger page sizes, the overhead is higher than with moderate pages, too.
The explanation for these higher overheads is that large pages have a higher
commit cost. Even if an application accesses few memory locations, \sys pages
data at full page size, degrading performance by sometimes paging in and out
unnecessary data.  The data reveal a reasonable default page size of 64 bytes
and when developing an application, a developer should consider varying the
page size to moderate poor performance.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/pagSizeOverhead}
	\includegraphics[width=\columnwidth]{figures/pagefault}
	\caption{\sys's page size affects overhead and page fault count.}
	\label{fig:IPOSPerformance}
	\label{fig:page_size}
\end{figure}

>>>>

We evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp} energy-harvesting
platform build around a MSP430FR5969~\cite{wolverine} MCU with 64\,kB of FRAM.
We used a TI Flash Emulation Tool (FET)~\cite{fet} as a power supply during
experiments with continuous power. For energy measurements, we used
EDB~\cite{edb}. In experiments with wireless power, we powered the WISP using
an RFID reader (Impinj R1000 with firmware version
3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ
8\,dBic~\cite{atlas2015}. We controlled the RFID reader from a workstation
running Ubuntu 10.4 using \emph{sllurp}~\cite{sllrp_github}. We set the
transmitted power of the RFID reader to 30\,dBm at 915\,MHz center frequency.
For distance-controlled experiments, we affixed the WISP at varying lengths to
hollow paper tubes placed flat on a lying antenna. Timing measurements
were done using the Salea~\cite{saleae} logic analyzer.

For some experiments (noted below) we used an alternative setup where the
MSP-TS430RGZ48C launchpad was used for continuous power experiments and used
internal timer for measuring run time. For harvested energy, we used
WISP\,5.0~\cite{wisp5,wisp} hardware and ThingMagic Astra-EX integrated RFID
reader set at 30\,dBm transmission power at 915\,MHz. We used EDB~\cite{edb}
to measure run time. Applications were cross-compiled using GCC and Clang (both version 3.8.0), allowing us to use LLVM for the \sys compiler.

@@

We evaluated \sys using benchmarks from the literature~\cite{chain,alpaca} and
several new programs: (i) \textbf{bc}: counts bits in byte pseudo-random string
using several algorithms, and compares results for correctness; (ii)
\textbf{cem}, which emulates an embedded temperature sensing engine and in
which measurements are randomly generated and compressed using LZW with a fixed
entry dictionary and fixed byte block; (iii) \textbf{cuckoo}: which implements
a Bloom-filter-like Cuckoo filter that first hashes a sequence of pseudo-random
numbers, then queries the filter to recover the sequence; (iv) \textbf{rsa}:
which encrypts a fixed string with a stored key; (v) \textbf{ar}: which
performs nearest neighbour classification of randomly generated data modelling a
three-axis accelerometer. This set of benchmarks overlaps with those used
in~\cite{chain,alpaca}. We implemented several new applications: (vi)
\textbf{sort}: selection sort algorithm on a fixed sequence of numbers, and
(vii) \textbf{dft}: discrete Fourier transform. All applications are compared
in columns eight and nine of Table~\ref{table:compiler_result} showing the
number of source lines of code compared to Chain.

@@

We evaluated \sys to show that it is easy to use and efficient across our
benchmarks. %We evaluate \sys's ease of use by characterizing \sys's automatic task compiler. We evaluate \sys efficiency by comparing its runtime performance to Chain. We characterize \sys by studying how its performance varies due to coalescing and when using automatic task compilation versus manual task compilation.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalStrategies}
	\caption{\sys coalescing performance measured per application on fixed power (left-most bar per application) and at 20 cm and 40 cm from the RFID reader (center and right-most two bars per application) compared to \sys without coalescing.}
	\label{fig:coalescing}
\end{figure}

@@

We evaluated the effect that paging with different page sizes has on \sys's
performance and we show data in Figure~\ref{fig:page_size}. We show two plots:
the top plot shows the run time performance normalized to the best
per-application performance, using pages of different sizes in \sys, indicated
with the labels on top of each cem bar; the bottom plot shows the number of
page faults for the same set of executions normalized to the maximum of each
set.
%
We measured performance as MCU clock cycles using values read out by TI's CCS
IDE. 
%
The results show a clear ``bathtub curve'' in the performance of each
application, as the number of page faults varies. The data show that across
application there is a page size that minimizes \emph{both} execution time.  We
observe that the page size is not the same for each application, although 64
byte pages perform well for all applications. The increased rate of
page faults is responsible for the overhead with small page sizes; smaller
pages require accessing more different pages, leading to higher paging costs.
With larger page sizes, the overhead is higher than with moderate pages, too.
The explanation for these higher overheads is that large pages have a higher
commit cost. Even if an application accesses few memory locations, \sys pages
data at full page size, degrading performance by sometimes paging in and out
unnecessary data.  The data reveal a reasonable default page size of 64 bytes
and when developing an application, a developer should consider varying the
page size to moderate poor performance.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/ramPagsSizes}
	\includegraphics[width=\columnwidth]{figures/pagefault}
	\caption{\sys's page size affects overhead and page fault count.}
	\label{fig:IPOSPerformance}
	\label{fig:page_size}
\end{figure}
